SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-27 scipy-1.0/paper.tex
Address comment of @mdhaber on Impact Now section.

\texttt{scipy.sparse} offers seven sparse matrix data structures. 
The most important ones are CSR and CSC; these offer fast row or column 
access and fast matrix-vector multiplication, and are used heavily in 
scikit-learn.

Over the last three years our sparse matrix handling internals have
been rewritten and performance has been improved. Iterating over 
and slicing of CSC and CSR matrices is now faster by up to 35\%,
and the CSR to COO matrix format conversion is now several times faster.
COO matrices are now generally more memory efficient. Importantly,
SuperLU\cite{superlu_ug99} was updated to version 5.2.1, enhancing
the low-level implementations leveraged by a subset of our \texttt{sparse}
offerings.

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (@) operator when
available. We've added \texttt{scipy.sparse.norm} and \texttt{scipy.sparse.random} 
for computing sparse matrix norms and drawing random variates from arbitrary 
distributions, respectively.

@@

From the user side, there were 13,096,468 PyPI downloads
of SciPy during the year 2017\cite{pypinfo}, which is likely a vast
underestimate of total downloads given that we don't have access to the
popular Anaconda package manager download statistics. The recommended 
source for citing SciPy is simply a reference to the website / library
itself\cite{SciPylib}, and has been cited $>3000$ times. Some of the most
prominent usages of or demonstrations of credibility for SciPy include the LIGO / Virgo
scientific collaboration that lead to the observation of gravitational
waves \cite{PhysRevLett.116.061102}, and the fact that SciPy is shipped directly
with MacOS and in the Intel Distribution for Python\cite{intel-python}.

>>>>

@@

From the user side, there were 13,096,468 downloads of SciPy from the
Python Packaging Index (PyPI) during the year 2017\cite{pypinfo}, which is
a lower bound on the number of total downloads by users given that downloading
from PyPI is only one of several popular methods to install SciPy.
The SciPy website\cite{SciPylib}, which has been the default citation in the
absence of a peer-reviewed paper, has been cited $>3000$ times. Some of the most
prominent usages of or demonstrations of credibility for SciPy include the LIGO / Virgo
scientific collaboration that lead to the observation of gravitational
waves \cite{PhysRevLett.116.061102}, and the fact that SciPy is shipped directly
with MacOS and in the Intel Distribution for Python\cite{intel-python}.
